---
title: "BootStrap"
author: "Marvin Scott"
date: "June 27, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
###    Write bootstrap code to illustrate the central limit theorem in R markdown 
###    Use a normal distribution with two different sample sizes.


###### **BootStrap Procedure Sample size 25  from Normal Distribution**
```{r echo=TRUE}
## Assign Sample to Varible 
w<-rnorm(25, 9, 1.97)
p<-1000
brnorm<- numeric(p)
###Function executed for 1000 loops/samplings 
for (i in 1:p) {
nmsample<- sample(w, size = 25, replace = TRUE)
brnorm[i]<- mean(nmsample)
}
brnorm
```


###### **BootStrap Procedure Sample size 85**
```{r echo=TRUE}
## Assign Sample to Varible 
w<-rnorm(85, 9, 1.97)
p<-1000
brnorm<- numeric(p)
###Function executed for 1000 loops/samplings 
for (i in 1:p) {
nmsample<- sample(w, size = 85, replace = TRUE)
brnorm[i]<- mean(nmsample)
}
brnorm
```


###### *NOTE:* BootStrap Procedure gives proof of the Central Limit Theroem, IE noraml distribution.
```{r  echo=TRUE}
hist(brnorm)
qqnorm(brnorm)

```




###### **BootStrap Procedure Sample size 20  from Exponential Distribution**
```{r echo=TRUE}
## Assign Sample to Varible 
w<-rexp(20)
p<-1000
brexp<- numeric(p)
###Function executed for 1000 loops/samplings 
for (i in 1:p) {
rexpsample<- sample(w, size = 20, replace = TRUE)
brexp[i]<- mean(rexpsample)
}
brexp
```


###### **BootStrap Procedure Sample size 80**
```{r echo=TRUE}
## Assign Sample to Varible 
w<-rexp(80)
p<-1000
brexp<- numeric(p)
###Function executed for 1000 loops/samplings 
for (i in 1:p) {
rexpsample<- sample(w, size = 80, replace = TRUE)
brexp[i]<- mean(rexpsample)
}
brexp
```



###### *NOTE:* BootStrap Procedure gives proof of the Central Limit Theroem, IE noraml distribution.
```{r  echo=TRUE}
hist(brexp)
qqnorm(brexp)

```


